---
title: "2017.12 Larval Anthracene 48 h fragmentation"
author: "Mikaela Nordborg"
date: "22/02/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(dplyr)
library(bayesnec) #devtools::install_github("open-AIMS/bayesnec")
require(tidyverse)
library(beepr)
inv.log10 <- function(x){10^x}
```

Replace: 
    .frag48 -> as appropriate for the endpoint
    _frag48 -> as appropriate for the endpoint
    Ant.17Dec -> as appropriate for the current data set
    2017.12_Ant -> as appropriate for the current data set
    EC10 -> as appropriate for current data set (have to go through each individual occurrance a some are used in plotting and extract result-functions)
    EC50 -> as appropriate for current data set ('replace all' can be used)


## Background
Analysis of data sets from A. millepora planula larvae experiments performed between 2016 and 2019 to test the effects of filtered seawater (FSW) solutions containing individual aromatic hydrocarbons in the presence and absence of ultraviolet radiation (+UV vs -UV). All analysis performed in (at least) four steps:
    - Model fitting, evaluation and interpretation of -UVR/PAR only treatment data
    - Model fitting, evaluation and interpretation of +UVR treatment data
    - Extraction of no effect concentration (NEC), 10 and 50% effect or lethal concentrations (EC/LCx) and associated 95% credible intervals.
    - Comparison of posterior distributions of extracted NEC and 50% threshold concentrations for each light treatment (+/-UV).

Compromised or invalid replicates identified prior to data import into R but removal is performed after import. Please see methods of main paper and *Table ___*, Supplementary materials for further details. Control treatment concentration-values set to 0.1 (~1/2 of the lowest treatment concentration used across all assays) to avoid potential issues with transformations after data import.Treatment concentrations log10 transformed and analysed on log-scale due to the spacing of treatment concentrations and range covered (equal to or larger than 3 orders of magnitude).


A majority of the data sets consist of binomial data and the following terms are used throughout:
    year = year and month experiment was performed
    endpoint = endpoint assessed
    factor = light treatment used
        PAR = -UVR/in the absence of UV light
        UV = +UVR/in the presence of UV light
    nom.x = nominal treatment or treatment concentration used (eg FSW or 0.01% DMSO controls)
    raw.x = time averaged, measured treatment concentration in μg L-1
    log.x = transformed, time-averaged, treatment concentrations (measured in μg L-1)
    suc = number of successes in sample (ie number of average sized larvae), generally a log10-transformation used
    tot = total number of organisms/larvae & recruits in sample at time of assessment
    prop = proportion of successes out of total tries/larvae in the sample


Data for some compounds available for several years and/or months. Each data set was analysed separately.


Analysis performed by Mikaela Nordborg and Dr. Rebecca Fisher.


## Packages used and installation of latest version of bayesnec

Analysis performed using package bayesnec and it's dependencies in R Version 4.0.3. The latest version of bayesnec and all dependencies were installed prior to start of analysis (23 April 2021).



## Analysis

### Import data, perform data preparation and check data types

Import data, wrangle and do quick initial checks
```{r}
data.Ant.17Dec.frag48.raw<- read_csv("Data/2017.12_AM_anth_frags48h.csv") %>% 
  data.frame() %>% 
  dplyr::mutate(raw.x=as.numeric(as.character(raw.x)),
                raw.x=ifelse(raw.x==0, 0.1, raw.x), # deal with 0 concentration values
                nom.x=as.factor(as.character(nom.x)),
                factor=as.factor(as.character(factor)),
                suc=as.integer(suc), # ensure integers
                log.x=log10(raw.x), # create log values (doesn't really matter if it's log or log10() unless there's a difference in the scaling of the x-data)
                tot=as.integer(tot))


save(data.Ant.17Dec.frag48.raw, file = "2017.12_Ant_data_frag48_raw.RData")

#Check that all columns have been assigned the correct data type & that adding 0.1 to raw.x controls worked
str(data.Ant.17Dec.frag48.raw)
head(data.Ant.17Dec.frag48.raw)
tail(data.Ant.17Dec.frag48.raw)
```


Check for differences between 0.01% DMSO and FSW controls
```{r}
load("2017.12_Ant_data_frag48_raw.RData")

#Remove treatment replicates from data set
data.Ant.17Dec.frag48.controls <- data.Ant.17Dec.frag48.raw %>% 
  dplyr::filter(nom.x!="Treatment")

#Plot to compare means and CIs
ggplot(data.Ant.17Dec.frag48.controls, aes(x=nom.x, y=prop, fill=factor)) + 
    geom_boxplot()

#Filer in preparation for t-tests
Ant.17Dec.frag48.controls.PAR.FSW <- data.Ant.17Dec.frag48.controls %>% 
  dplyr::filter(factor=="PAR" & nom.x=="FSW")
Ant.17Dec.frag48.controls.PAR.DMSO <- data.Ant.17Dec.frag48.controls %>% 
  dplyr::filter(factor=="PAR" & nom.x!="FSW")

Ant.17Dec.frag48.controls.UV.FSW <- data.Ant.17Dec.frag48.controls %>% 
  dplyr::filter(factor=="UVR" & nom.x=="FSW")
Ant.17Dec.frag48.controls.UV.DMSO <- data.Ant.17Dec.frag48.controls %>% 
  dplyr::filter(factor=="UVR" & nom.x!="FSW")

#Perform t-test to check for differences between control groups
brms.fit <- brm(suc | trials(tot)  ~ nom.x*factor, data = data.Ant.17Dec.frag48.controls, family = binomial())
new.dat <- data.frame(expand.grid(list(nom.x=c("FSW", "0.01% DMSO"),  "factor"=c("UVR", "PAR"),"tot"=1)))
post_preds <- posterior_epred(brms.fit, newdata=new.dat) %>% 
  data.frame

colnames(post_preds) <- paste(new.dat$nom.x, new.dat$factor)
pred_dat <-  post_preds %>% 
  pivot_longer(everything())

ggplot(pred_dat, aes(x=value)) + 
  geom_density(aes(group=name, colour=name, fill = name), alpha=0.3) +
  scale_x_continuous(labels = scales::percent, name ="Average 48 h fragmentation success") +
  scale_y_continuous(name ="Posterior probability density") +
  theme_classic() 
```


Invert and calculate the mean 48 h fragmentation using the posterior probability for each data set
```{r}
1-mean(post_preds[,1]) #FSW UVR
1-mean(post_preds[,2]) #0.01% DMSO UVR
1-mean(post_preds[,3]) #FSW PAR
1-mean(post_preds[,4]) #0.01% DMSO PAR
```

Extract the median proportion of larvae that were of average size using the posterior probability for each control data set
```{r}
quantile(post_preds[,1], c(0.025, 0.5, 0.975)) #FSW UVR
quantile(post_preds[,2], c(0.025, 0.5, 0.975)) #0.01% DMSO UVR
quantile(post_preds[,3], c(0.025, 0.5, 0.975)) #FSW PAR
quantile(post_preds[,4], c(0.025, 0.5, 0.975)) #0.01% DMSO PAR
```


Filter remaining data according to light treatment + whether replicates should be included in statistical analysis and save to RData-files:
```{r}
load("2017.12_Ant_data_frag48_raw.RData")

#Remove FSW control replicates
data.Ant.17Dec.frag48 <- data.Ant.17Dec.frag48.raw %>% 
  dplyr::filter(nom.x!="FSW")

#Create -UVR data set and prep for use in model fitting
data.Ant.17Dec.frag48.PAR.raw <- data.Ant.17Dec.frag48 %>% 
  dplyr::filter(factor=="PAR") 
data.Ant.17Dec.frag48.PAR <- data.Ant.17Dec.frag48.PAR.raw %>% 
  dplyr::filter(use_in_model=="Yes") 

#Create +UVR data set and prep for use in model fitting
data.Ant.17Dec.frag48.UV.raw <- data.Ant.17Dec.frag48 %>% 
  dplyr::filter(factor=="UVR") 
data.Ant.17Dec.frag48.UV <- data.Ant.17Dec.frag48.UV.raw %>% 
  dplyr::filter(use_in_model=="Yes") 

#check that filtering worked
View(data.Ant.17Dec.frag48.PAR)
View(data.Ant.17Dec.frag48.UV)

#Save complete data sets and data sets prepared for model fitting
save(data.Ant.17Dec.frag48.PAR.raw, data.Ant.17Dec.frag48.UV.raw, data.Ant.17Dec.frag48.PAR,data.Ant.17Dec.frag48.UV, file = "2017.12_Ant_data_frag48_filtered.RData")

load(file = "2017.12_Ant_data_frag48_filtered.RData")
```

----------------------------------------------------------------
----------------------------------------------------------------


### -UV/PAR

#### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2017.12_Ant_data_frag48_filtered.RData")

unique(data.Ant.17Dec.frag48.PAR$raw.x)
par(mfrow=c(2,1))
hist(data.Ant.17Dec.frag48.PAR$raw.x)
hist(data.Ant.17Dec.frag48.PAR$suc/data.Ant.17Dec.frag48.PAR$tot)
par(mfrow=c(1,1))
plot(data.Ant.17Dec.frag48.PAR$log.x, data.Ant.17Dec.frag48.PAR$prop) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


##### Fit models


###### Binomial

Fit a model-averaged NEC-model (MANEC)
```{r, eval=FALSE}
load(file = "2017.12_Ant_data_frag48_filtered.RData")
library(bayesnec)
library(beepr)
out.Ant.17Dec.frag48.PAR.all <- bnec(data = data.Ant.17Dec.frag48.PAR, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all")
save(out.Ant.17Dec.frag48.PAR.all, file = "2017.12_Ant_frag48_PAR_modfit_all.RData")
beep("mario")
```

Check RHat values to discard bad candidate model fits
```{r}
load("2017.12_Ant_frag48_PAR_modfit_all.RData")

rhat(out.Ant.17Dec.frag48.PAR.all, rhat_cutoff = 1.03)
```

Drop candidate models that failed the RHat test (if required)
```{r}
load("2017.12_Ant_frag48_PAR_modfit_all.RData")

out.Ant.17Dec.frag48.PAR.all2 <- amend(out.Ant.17Dec.frag48.PAR.all, drop = c("neclinhorme", "ecxll5")) #add in bad candidate models in drop = c())
save(out.Ant.17Dec.frag48.PAR.all, out.Ant.17Dec.frag48.PAR.all2, file = "2017.12_Ant_frag48_PAR_modfit_all.RData")
```


Check overdispersion estimates and candidate model weights
```{r}
load("2017.12_Ant_frag48_PAR_modfit_all.RData")

out.Ant.17Dec.frag48.PAR.all2$mod_stats
summary(out.Ant.17Dec.frag48.PAR.all2)
```

*Any evidence of overdispersion?*
    - All candidate models show some overdispersion.


```{r}
plot(out.Ant.17Dec.frag48.PAR.all2, add_ec10 = TRUE, add_nec = FALSE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```



###### Betabinomial

Re-fit MANEC using a distribution appropriate for overdispersed binomial data
```{r}
load(file = "2017.12_Ant_data_frag48_filtered.RData")
library(bayesnec)
library(beepr)
out.Ant.17Dec.frag48.PAR.all.od <- bnec(data = data.Ant.17Dec.frag48.PAR, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all",
                        family = beta_binomial2)

save(out.Ant.17Dec.frag48.PAR.all.od, file = "2017.12_Ant_frag48_PAR_modfit_all_OD.RData")
beep("mario")
```

No candidate models could be successfully fitted using the betabinomial distribution.



*As no candidate models could be successfully fitted using thebetabinomial distribution the MANEC fitted using the binomial distribution was used for extraction of results*




Check chain mixing
```{r}
load("2017.12_Ant_frag48_PAR_modfit_all.RData")

check_chains(out.Ant.17Dec.frag48.PAR.all2, filename = "2017.12_Ant_frag48_PAR_chains_modfit_all") #change to out.Ant.17Dec.frag48.PAR.all2 if any models were dropped based on rhat
```

If dispersion estimate credible intervals do not include 1 the data is overdispersed. Investigate the chain mixing- and correlation plots further if RHat values >1.004 for any parameter. If all models fail the RHat test (ie all > 1.05): may need to re-fit the MANEC with increased iterations or burn-in.

*Any evidence of non-convergence, poor chain mixing or autocorrelation?*
    - No


Check if model median, credible intervals and NEC estimates are reasonable for candidate models compared to the raw data
```{r}
load("2017.12_Ant_frag48_PAR_modfit_all.RData")

pdf("2017.12_Ant_frag48_PAR_modfitplots_all.pdf")
plot(out.Ant.17Dec.frag48.PAR.all2, all_models = TRUE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
dev.off()
```




Check the modified MANEC fit
```{r}
plot(out.Ant.17Dec.frag48.PAR.all2, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```


Rename model output for selected model (binomial or betabinomial)
```{r}
out.Ant.17Dec.frag48.PAR <- out.Ant.17Dec.frag48.PAR.all2
```


Extract the NEC-model subset for use in extraction of NEC and comparisons of posterior distributions
```{r}
out.Ant.17Dec.frag48.PAR.NEC <- pull_out(out.Ant.17Dec.frag48.PAR, model = c("nec"))
```


```{r}
plot(out.Ant.17Dec.frag48.PAR.NEC, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```


Save the output for the selected models
```{r}
save(out.Ant.17Dec.frag48.PAR, out.Ant.17Dec.frag48.PAR.NEC, file = "2017.12_Ant_frag48_PAR_modfits_final.RData")
load("2017.12_Ant_frag48_PAR_modfits_final.RData")
```



#### Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required
```{r}
load("2017.12_Ant_frag48_PAR_modfits_final.RData")
NEC.Ant.17Dec.frag48.PAR <- out.Ant.17Dec.frag48.PAR.NEC$w_nec
NEC.Ant.17Dec.frag48.PAR <- 10^NEC.Ant.17Dec.frag48.PAR #if using log10(raw.x)
#NEC.Ant.17Dec.frag48.PAR <- exp(NEC.Ant.17Dec.frag48.PAR) #if using log(raw.x)
NEC.Ant.17Dec.frag48.PAR
```

```{r}
load("2017.12_Ant_frag48_PAR_modfits_final.RData")
EC10.Ant.17Dec.frag48.PAR <- ecx(out.Ant.17Dec.frag48.PAR, ecx_val = 10, type = "absolute")
EC10.Ant.17Dec.frag48.PAR <- 10^EC10.Ant.17Dec.frag48.PAR #if using log10(raw.x)
#EC10.Ant.17Dec.frag48.PAR <- exp(EC10.Ant.17Dec.frag48.PAR) #if using log(raw.x)
EC10.Ant.17Dec.frag48.PAR
```

```{r}
load("2017.12_Ant_frag48_PAR_modfits_final.RData")
EC50.Ant.17Dec.frag48.PAR <- ecx(out.Ant.17Dec.frag48.PAR, ecx_val = 50, type = "absolute")
EC50.Ant.17Dec.frag48.PAR <- 10^EC50.Ant.17Dec.frag48.PAR #if using log10(raw.x)
#EC50.Ant.17Dec.frag48.PAR <- exp(EC50.Ant.17Dec.frag48.PAR) #if using log(raw.x)
EC50.Ant.17Dec.frag48.PAR
```


----------------------------------------------------------------
----------------------------------------------------------------


### +UV/UV

#### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2017.12_Ant_data_frag48_filtered.RData")

unique(data.Ant.17Dec.frag48.UV$raw.x)
par(mfrow=c(2,1))
hist(data.Ant.17Dec.frag48.UV$raw.x)
hist(data.Ant.17Dec.frag48.UV$suc/data.Ant.17Dec.frag48.UV$tot)
par(mfrow=c(1,1))
plot(data.Ant.17Dec.frag48.UV$log.x, data.Ant.17Dec.frag48.UV$prop) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


##### Fit models

###### Binomial

Fit a model-averaged NEC-model (MANEC)
```{r, eval=FALSE}
load(file = "2017.12_Ant_data_frag48_filtered.RData")

library(bayesnec)
library(beepr)
out.Ant.17Dec.frag48.UV.all <- bnec(data = data.Ant.17Dec.frag48.UV, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all")

save(out.Ant.17Dec.frag48.UV.all, file = "2017.12_Ant_frag48_UV_modfit_all.RData")
beep("mario")
```


Check RHat values to discard bad candidate model fits
```{r}
load("2017.12_Ant_frag48_UV_modfit_all.RData")

rhat(out.Ant.17Dec.frag48.UV.all, rhat_cutoff = 1.03)
```

Drop candidate models that failed the RHat test (if required)
```{r}
load("2017.12_Ant_frag48_UV_modfit_all.RData")

out.Ant.17Dec.frag48.UV.all2 <- amend(out.Ant.17Dec.frag48.UV.all, drop = c("ecxwb2")) #add in bad candidate models in drop = c())
save(out.Ant.17Dec.frag48.UV.all, out.Ant.17Dec.frag48.UV.all2, file = "2017.12_Ant_frag48_UV_modfit_all.RData")
```


Check overdispersion estimates and candidate model weights
```{r}
load("2017.12_Ant_frag48_UV_modfit_all.RData")

out.Ant.17Dec.frag48.UV.all2$mod_stats
summary(out.Ant.17Dec.frag48.UV.all2)
```

*Any evidence of overdispersion?*
    - All candidate models show evidence of overdisperion.



```{r}
plot(out.Ant.17Dec.frag48.UV.all2, add_ec10 = FALSE, add_nec = FALSE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```


###### Betabinomial

Re-fit MANEC using a distribution appropriate for overdispersed binomial data
```{r}
load(file = "2017.12_Ant_data_frag48_filtered.RData")
library(bayesnec)
library(beepr)
out.Ant.17Dec.frag48.UV.all.od <- bnec(data = data.Ant.17Dec.frag48.UV, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all",
                        family = beta_binomial2)

save(out.Ant.17Dec.frag48.UV.all.od, file = "2017.12_Ant_frag48_UV_modfit_all_OD.RData")
beep("mario")
```


Check RHat values to discard bad candidate model fits
```{r}
load("2017.12_Ant_frag48_UV_modfit_all_OD.RData")

rhat(out.Ant.17Dec.frag48.UV.all.od, rhat_cutoff = 1.03)
```



Check chain mixing for remaining candidate models
```{r}
load("2017.12_Ant_frag48_UV_modfit_all_OD.RData")

check_chains(out.Ant.17Dec.frag48.UV.all.od, filename = "2017.12_Ant_frag48_UV_chains_modfit_all_OD") #change this if any candidate models were discarded based on Rhat: out.Ant.17Dec.frag48.UV.all.od2
out.Ant.17Dec.frag48.UV.all.od$mod_stats
summary(out.Ant.17Dec.frag48.UV.all.od)
```

*Any evidence of non-convergence, poor chain mixing or autocorrelation?*
    - model =       include/unclear/exclude     (reason for potential exclusion)
    
    - Most of the candidate models show some evidence of instability.


```{r}
plot(out.Ant.17Dec.frag48.UV.all.od, add_ec10 = FALSE, add_nec = FALSE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```

    
Check if model median, credible intervals and NEC estimates are reasonable for candidate models compared to the raw data
```{r}
load("2017.12_Ant_frag48_UV_modfit_all_OD.RData")
pdf("2017.12_Ant_frag48_UV_modfitplots_all_OD.pdf")
plot(out.Ant.17Dec.frag48.UV.all.od, all_models = TRUE, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
dev.off()
```


###### Compare binomial and betabinomial MANECs and select model to use

Compare to MANEC fitted using the binomial distribution
```{r}
plot(out.Ant.17Dec.frag48.UV.all2, add_ec10 = FALSE, add_nec = FALSE, lxform = inv.log10)
plot(out.Ant.17Dec.frag48.UV.all.od, add_ec10 = FALSE, add_nec = FALSE, lxform = inv.log10)
```


*Did using the betabinomial distribution improve MANEC model fit compared to the MANEC fit using the binomial distribution?*
    - Yes, it widened the credible intervals.


Rename model output for selected model (binomial or betabinomial)
```{r}
out.Ant.17Dec.frag48.UV <- out.Ant.17Dec.frag48.UV.all.od
```


Extract the NEC-model subset for use in extraction of NEC and comparisons of posterior distributions
```{r}
out.Ant.17Dec.frag48.UV.NEC <- pull_out(out.Ant.17Dec.frag48.UV, model = c("nec"))
```


```{r}
plot(out.Ant.17Dec.frag48.UV.NEC, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```


Save the output for the selected models
```{r}
save(out.Ant.17Dec.frag48.UV, out.Ant.17Dec.frag48.UV.NEC, file = "2017.12_Ant_frag48_UV_modfits_final.RData")
load("2017.12_Ant_frag48_UV_modfits_final.RData")
```



#### Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required
```{r}
load("2017.12_Ant_frag48_UV_modfits_final.RData")
NEC.Ant.17Dec.frag48.UV <- out.Ant.17Dec.frag48.UV.NEC$w_nec
NEC.Ant.17Dec.frag48.UV <- 10^NEC.Ant.17Dec.frag48.UV #if using log10(raw.x)
#NEC.Ant.17Dec.frag48.UV <- exp(NEC.Ant.17Dec.frag48.UV) #if using log(raw.x)
NEC.Ant.17Dec.frag48.UV
```

```{r}
load("2017.12_Ant_frag48_UV_modfits_final.RData")
EC10.Ant.17Dec.frag48.UV <- ecx(out.Ant.17Dec.frag48.UV, ecx_val = 10, type = "absolute")
EC10.Ant.17Dec.frag48.UV <- 10^EC10.Ant.17Dec.frag48.UV #if using log10(raw.x)
#EC10.Ant.17Dec.frag48.UV <- exp(EC10.Ant.17Dec.frag48.UV) #if using log(raw.x)
EC10.Ant.17Dec.frag48.UV
```

```{r}
load("2017.12_Ant_frag48_UV_modfits_final.RData")
EC50.Ant.17Dec.frag48.UV <- ecx(out.Ant.17Dec.frag48.UV, ecx_val = 50, type = "absolute")
EC50.Ant.17Dec.frag48.UV <- 10^EC50.Ant.17Dec.frag48.UV #if using log10(raw.x)
#EC50.Ant.17Dec.frag48.UV <- exp(EC50.Ant.17Dec.frag48.UV) #if using log(raw.x)
EC50.Ant.17Dec.frag48.UV
```

----------------------------------------------------------------
----------------------------------------------------------------


### Compare light treatments and pLot results

```{r}
#For plotting results & model/threshold value comparisons
library(ggplot2)
library(scales)
library(tidybayes)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```


Extract complete posteriors for the fitted values using compare_posterior-function
```{r}
load("2017.12_Ant_frag48_PAR_modfits_final.RData")
load("2017.12_Ant_frag48_UV_modfits_final.RData")

pred.Ant.17Dec.frag48 <- compare_posterior(x=list("PAR" = out.Ant.17Dec.frag48.PAR, "UVR" = out.Ant.17Dec.frag48.UV), comparison = "fitted", precision = 50)

pred.Ant.17Dec.frag48.PAR <- pred.Ant.17Dec.frag48$posterior_data %>% 
  dplyr::filter(model=="PAR")

pred.Ant.17Dec.frag48.UV <- pred.Ant.17Dec.frag48$posterior_data %>% 
  dplyr::filter(model=="UVR")



pred.Ant.17Dec.frag48.NEC <- compare_posterior(list("PAR" = out.Ant.17Dec.frag48.PAR.NEC, "UVR" = out.Ant.17Dec.frag48.UV.NEC), comparison = "fitted", precision = 50)

pred.Ant.17Dec.frag48.PAR.NEC <- pred.Ant.17Dec.frag48.NEC$posterior_data %>% 
  dplyr::filter(model=="PAR")
pred.Ant.17Dec.frag48.UV.NEC <- pred.Ant.17Dec.frag48.NEC$posterior_data %>% 
 dplyr::filter(model=="UVR")


save(pred.Ant.17Dec.frag48, pred.Ant.17Dec.frag48.PAR, pred.Ant.17Dec.frag48.UV, pred.Ant.17Dec.frag48.PAR.NEC, pred.Ant.17Dec.frag48.UV.NEC, file = "2017.12_Ant_frag48_predvals.RData") 

load("2017.12_Ant_frag48_predvals.RData")
str(pred.Ant.17Dec.frag48.PAR)
str(pred.Ant.17Dec.frag48.UV)
```


#### Plot MANEC model fits alongside raw data
##### Complete subset-MANEC plot

Invert model median and credible intervals
```{r}
pred.Ant.17Dec.frag48.PAR.inv <- as.data.frame(pred.Ant.17Dec.frag48.PAR)
head(pred.Ant.17Dec.frag48.PAR.inv)
pred.Ant.17Dec.frag48.PAR.inv <- mutate(pred.Ant.17Dec.frag48.PAR.inv, Estimate = 1-(pred.Ant.17Dec.frag48.PAR.inv$Estimate))
pred.Ant.17Dec.frag48.PAR.inv <- mutate(pred.Ant.17Dec.frag48.PAR.inv, Q97.5 = 1-(pred.Ant.17Dec.frag48.PAR.inv$Q97.5))
pred.Ant.17Dec.frag48.PAR.inv <- mutate(pred.Ant.17Dec.frag48.PAR.inv, Q2.5 = 1-(pred.Ant.17Dec.frag48.PAR.inv$Q2.5))
head(pred.Ant.17Dec.frag48.PAR.inv)
```

```{r}
pred.Ant.17Dec.frag48.UV.inv <- as.data.frame(pred.Ant.17Dec.frag48.UV)
head(pred.Ant.17Dec.frag48.UV.inv)
pred.Ant.17Dec.frag48.UV.inv <- mutate(pred.Ant.17Dec.frag48.UV.inv, Estimate = 1-(pred.Ant.17Dec.frag48.UV.inv$Estimate))
pred.Ant.17Dec.frag48.UV.inv <- mutate(pred.Ant.17Dec.frag48.UV.inv, Q97.5 = 1-(pred.Ant.17Dec.frag48.UV.inv$Q97.5))
pred.Ant.17Dec.frag48.UV.inv <- mutate(pred.Ant.17Dec.frag48.UV.inv, Q2.5 = 1-(pred.Ant.17Dec.frag48.UV.inv$Q2.5))
head(pred.Ant.17Dec.frag48.UV.inv)
```

Save inverted predicted values
```{r}
save(pred.Ant.17Dec.frag48, pred.Ant.17Dec.frag48.PAR, pred.Ant.17Dec.frag48.UV, pred.Ant.17Dec.frag48.PAR.NEC, pred.Ant.17Dec.frag48.UV.NEC, pred.Ant.17Dec.frag48.PAR.inv, pred.Ant.17Dec.frag48.UV.inv, file = "2017.12_Ant_frag48_predvals.RData") 
```



```{r}
load("2017.12_Ant_data_frag48_filtered.RData")
load("2017.12_Ant_frag48_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p.all= p.all+  geom_ribbon(aes(x=10^pred.Ant.17Dec.frag48.PAR.inv$x, ymin=pred.Ant.17Dec.frag48.PAR.inv$Q2.5, ymax=pred.Ant.17Dec.frag48.PAR.inv$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+  geom_ribbon(aes(x=10^pred.Ant.17Dec.frag48.UV.inv$x, ymin=pred.Ant.17Dec.frag48.UV.inv$Q2.5, ymax=pred.Ant.17Dec.frag48.UV.inv$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred.Ant.17Dec.frag48.PAR.inv$x, y=pred.Ant.17Dec.frag48.PAR.inv$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred.Ant.17Dec.frag48.UV.inv$x, y=pred.Ant.17Dec.frag48.UV.inv$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = data.Ant.17Dec.frag48.PAR, aes(x = raw.x, y = prop, colour=factor(factor), shape = factor(factor), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.02))
p.all= p.all+ geom_point(data = data.Ant.17Dec.frag48.UV, aes(x = raw.x, y = prop, colour=factor(factor), shape = factor(factor), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.02))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~"L"^{-1})
              y=expression(48~h~fragmentation~("%")),
              subtitle="a)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue"))
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.09, 30000), trans="log10", breaks = c(0.1, 1, 10, 100, 1000, 10000), labels = c(0, 1, 10, 100, 1000, 10000))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot.Ant.17Dec.frag48.all <- p.all
plot.Ant.17Dec.frag48.all
```


#### NEC subset-MANEC plot

Invert model median and credible intervals
```{r}
pred.Ant.17Dec.frag48.PAR.inv.NEC <- as.data.frame(pred.Ant.17Dec.frag48.PAR.NEC)
head(pred.Ant.17Dec.frag48.PAR.inv.NEC)
pred.Ant.17Dec.frag48.PAR.inv.NEC <- mutate(pred.Ant.17Dec.frag48.PAR.inv.NEC, Estimate = 1-(pred.Ant.17Dec.frag48.PAR.inv.NEC$Estimate))
pred.Ant.17Dec.frag48.PAR.inv.NEC <- mutate(pred.Ant.17Dec.frag48.PAR.inv.NEC, Q97.5 = 1-(pred.Ant.17Dec.frag48.PAR.inv.NEC$Q97.5))
pred.Ant.17Dec.frag48.PAR.inv.NEC <- mutate(pred.Ant.17Dec.frag48.PAR.inv.NEC, Q2.5 = 1-(pred.Ant.17Dec.frag48.PAR.inv.NEC$Q2.5))
head(pred.Ant.17Dec.frag48.PAR.inv.NEC)
```

```{r}
pred.Ant.17Dec.frag48.UV.inv.NEC <- as.data.frame(pred.Ant.17Dec.frag48.UV.NEC)
head(pred.Ant.17Dec.frag48.UV.inv.NEC)
pred.Ant.17Dec.frag48.UV.inv.NEC <- mutate(pred.Ant.17Dec.frag48.UV.inv.NEC, Estimate = 1-(pred.Ant.17Dec.frag48.UV.inv.NEC$Estimate))
pred.Ant.17Dec.frag48.UV.inv.NEC <- mutate(pred.Ant.17Dec.frag48.UV.inv.NEC, Q97.5 = 1-(pred.Ant.17Dec.frag48.UV.inv.NEC$Q97.5))
pred.Ant.17Dec.frag48.UV.inv.NEC <- mutate(pred.Ant.17Dec.frag48.UV.inv.NEC, Q2.5 = 1-(pred.Ant.17Dec.frag48.UV.inv.NEC$Q2.5))
head(pred.Ant.17Dec.frag48.UV.inv.NEC)
```

Save inverted predicted values
```{r}
save(pred.Ant.17Dec.frag48, pred.Ant.17Dec.frag48.PAR, pred.Ant.17Dec.frag48.UV, pred.Ant.17Dec.frag48.PAR.NEC, pred.Ant.17Dec.frag48.UV.NEC, pred.Ant.17Dec.frag48.PAR.inv, pred.Ant.17Dec.frag48.UV.inv, pred.Ant.17Dec.frag48.PAR.inv.NEC, pred.Ant.17Dec.frag48.UV.inv.NEC, file = "2017.12_Ant_frag48_predvals.RData") 
```




```{r}
load("2017.12_Ant_data_frag48_filtered.RData")
load("2017.12_Ant_frag48_predvals.RData")

p.NEC= ggplot()
p.NEC= p.NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p.NEC= p.NEC+  geom_ribbon(aes(x=10^pred.Ant.17Dec.frag48.PAR.inv.NEC$x, ymin=pred.Ant.17Dec.frag48.PAR.inv.NEC$Q2.5, ymax=pred.Ant.17Dec.frag48.PAR.inv.NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p.NEC= p.NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.NEC= p.NEC+  geom_ribbon(aes(x=10^pred.Ant.17Dec.frag48.UV.inv.NEC$x, ymin=pred.Ant.17Dec.frag48.UV.inv.NEC$Q2.5, ymax=pred.Ant.17Dec.frag48.UV.inv.NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p.NEC= p.NEC+  scale_fill_manual(values="steelblue")


p.NEC= p.NEC+ geom_line(aes(x=10^pred.Ant.17Dec.frag48.PAR.inv.NEC$x, y=pred.Ant.17Dec.frag48.PAR.inv.NEC$Estimate), color = 'grey30', size=0.5)
p.NEC= p.NEC+ geom_line(aes(x=10^pred.Ant.17Dec.frag48.UV.inv.NEC$x, y=pred.Ant.17Dec.frag48.UV.inv.NEC$Estimate), color = 'grey30', size=0.5)


p.NEC= p.NEC+ geom_point(data = data.Ant.17Dec.frag48.PAR, aes(x = raw.x, y = prop, colour=factor(factor), shape = factor(factor), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.02))
p.NEC= p.NEC+ geom_point(data = data.Ant.17Dec.frag48.UV, aes(x = raw.x, y = prop, colour=factor(factor), shape = factor(factor), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.02))


p.NEC = p.NEC+ labs(x=expression(Concentration~(μg~"L"^{-1})),
              y=expression(48~h~ fragmentation~("%")),
              subtitle="c)")
p.NEC= p.NEC+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.NEC= p.NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.NEC= p.NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p.NEC= p.NEC+ theme(legend.position="none")
# p.NEC = p.NEC  + theme(legend.position = c(0.9, 0.9))
p.NEC= p.NEC+ scale_x_continuous(limits = c(0.09, 30000), trans="log10", breaks = c(0.1, 1, 10, 100, 1000, 10000), labels = c(0, 1, 10, 100, 1000, 10000))
#p.NEC= p.NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot.Ant.17Dec.frag48.NEC <- p.NEC
plot.Ant.17Dec.frag48.NEC
```

----------------------------------------------------------------
----------------------------------------------------------------


### Compare +/-UV posteriors

#### Full model comparisons

Extract the highest probability that the fitted values/posteriors for the two light treatments are different (at any tested x-value):
```{r}
load("2017.12_Ant_frag48_predvals.RData")

diff.prob.Ant.17Dec.frag48 <- max(pred.Ant.17Dec.frag48$prob_diff$prob)
diff.prob.Ant.17Dec.frag48
```


Plot the probability of a difference between the UV and PAR light treatments across the treatment concentrations tested
```{r}
load("2017.12_Ant_frag48_predvals.RData")

pred.Ant.17Dec.frag48$prob_diff$inv.x <- 10^pred.Ant.17Dec.frag48$prob_diff$x

p.comp.prob= ggplot(pred.Ant.17Dec.frag48$prob_diff) +
                geom_line(aes(x=inv.x, prob, color="grey"), size=0.8)

p.comp.prob= p.comp.prob + scale_color_manual(values = c("grey")) +
                theme_light() +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80")) +
                theme(legend.position="none") 
    
p.comp.prob= p.comp.prob + scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) +
                scale_x_continuous(limits = c(0.09, 30000), trans="log10", breaks = c(0.1, 1, 10, 100, 1000, 10000), labels = c(0, 1, 10, 100, 1000, 10000)) +
                labs(x=expression(Treatment~concentration~(μg~"L"^{-1})),
                      y=expression(Probability~that~UVR~affected~toxicity~("%")),
                      subtitle="a)")

plot.Ant.17Dec.frag48.diff.prob <- p.comp.prob
plot.Ant.17Dec.frag48.diff.prob
```

    If solid line (probability) is higher than 95%/0.95 = UVR significantly increased toxicity at that treatment concentration


Plot the posterior difference estimate for the UV and PAR light treatments across the treatment concentrations tested
```{r}
load("2017.12_Ant_frag48_predvals.RData")

pred.Ant.17Dec.frag48$diff_data$inv.x <- 10^pred.Ant.17Dec.frag48$diff_data$x

p.comp.diff = ggplot(pred.Ant.17Dec.frag48$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.09, 30000), trans="log10", breaks = c(0.1, 1, 10, 100, 1000, 10000), labels = c(0, 1, 10, 100, 1000, 10000)) +
              labs(x=expression(Treatment~concentration~(μg~"L"^{-1})),
                  y=expression(Posterior~difference~estimate),
                  subtitle="a)")

plot.Ant.17Dec.frag48.diff.est <- p.comp.diff
plot.Ant.17Dec.frag48.diff.est
```

    If credible intervals (shaded grey area) includes 0 (dotted blue line) there is no significant difference between the two models at that treatment concentration.




#### EC50

Perform comparison of posterior distributions for 48 h fragmentation EC50
```{r}
load("2017.12_Ant_frag48_PAR_modfits_final.RData")
load("2017.12_Ant_frag48_UV_modfits_final.RData")

comp.Ant.17Dec.frag48.EC50 <- compare_posterior(x=list("PAR" = out.Ant.17Dec.frag48.PAR, "UVR" = out.Ant.17Dec.frag48.UV), comparison = "ecx", ecx_val = 50)
save(comp.Ant.17Dec.frag48.EC50, file = "2017.12_Ant_frag48_posterior_comp_EC50.RData")
comp.Ant.17Dec.frag48.EC50$prob_diff
```

    Table shows the % likelihood that the point estimate calculated (NEC, EC/EC10 or EC/EC50) for model A (in top row) is smaller than the point estimate calculated for model B, C, etc (in left hand column). 

*Is EC50 +UVR likely to be lower than the EC50 -UVR?*
    - Yes, with a likelihood of 91.05%


Create a custom results plot of the EC50 comparison
```{r}
load("2017.12_Ant_frag48_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp.Ant.17Dec.frag48.EC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(limits = c(-0.5, 12), name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 4.3), breaks = c(-1, 0, 1, 2, 3, 4), labels = c(0, 1, 10, 100, 1000, 10000)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 10.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 91.05%", x = 0.55, y = 8.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot.Ant.17Dec.frag48.EC50 <- p.comp.EC50
comp.plot.Ant.17Dec.frag48.EC50
```


Create a custom plot of the EC50 comparisons differences posterior density
```{r}
load("2017.12_Ant_frag48_posterior_comp_EC50.RData")

p.comp.EC50.diff = ggplot(comp.Ant.17Dec.frag48.EC50$diff_data, aes(x=diff)) +
  geom_density(aes(x=diff, fill = 'grey'), alpha=0.4) + 
  geom_vline(xintercept = 0, color = "steelblue3", lty = 2, size=0.75) + 
  theme_light()

p.comp.EC50.diff = p.comp.EC50.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
  scale_color_manual(values = c("grey","steelblue3")) + 
  theme(legend.position="none")
p.comp.EC50.diff = p.comp.EC50.diff + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50.diff = p.comp.EC50.diff + scale_y_continuous(name = "Differences posterior density") 
p.comp.EC50.diff = p.comp.EC50.diff + scale_x_continuous(name = "Standardized effect size") 


#Rename & show plot
comp.plot.Ant.17Dec.frag48.EC50.diff <- p.comp.EC50.diff
comp.plot.Ant.17Dec.frag48.EC50.diff
```


#### NEC

Perform comparison of posterior distributions for 48 h fragmentation NEC
```{r}
load("2017.12_Ant_frag48_PAR_modfits_final.RData")
load("2017.12_Ant_frag48_UV_modfits_final.RData")

comp.Ant.17Dec.frag48.NEC <- compare_posterior(x=list("PAR" = out.Ant.17Dec.frag48.PAR, "UVR" = out.Ant.17Dec.frag48.UV), comparison = "nec")
save(comp.Ant.17Dec.frag48.NEC, file = "2017.12_Ant_frag48_posterior_comp_NEC.RData")
comp.Ant.17Dec.frag48.NEC$prob_diff
```

    Table shows the % likelihood that the point estimate calculated (NEC, EC/EC10 or EC/EC50) for model A (in top row) is smaller than the point estimate calculated for model B, C, etc (in left hand column). 

*Is the NEC +UVR likely to be lower than the NEC -UVR?*
    - No, with a likelihood of 35.38%.


Create a custom results plot of the NEC comparison
```{r}
load("2017.12_Ant_frag48_posterior_comp_NEC.RData")

p.comp.NEC = ggplot(comp.Ant.17Dec.frag48.NEC$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.NEC = p.comp.NEC + stat_pointinterval(aes(y=0.00, x=value, group=model),.width=c(.66, .95), size=0.5) +
  theme_light()

p.comp.NEC = p.comp.NEC + scale_fill_manual(values=c("seagreen", "steelblue"))+
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey")) + theme(legend.position="none")
p.comp.NEC = p.comp.NEC + theme(panel.grid.major = element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(), panel.border=element_blank(), axis.line=element_line(colour="grey80"))

p.comp.NEC = p.comp.NEC + scale_y_continuous(limits = c(-0.5, 12), name="Posterior probability density") 
p.comp.NEC = p.comp.NEC + scale_x_continuous(limits = c(-1.02, 4.3), breaks = c(-1, 0, 1, 2, 3, 4), labels = c(0, 1, 10, 100, 1000, 10000)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.NEC = p.comp.NEC + labs(x=expression(Threshold~concentration~(μg~"L"^{-1})),
               subtitle="d)")

p.comp.NEC= p.comp.NEC+ annotate("text", label = expression(Probability~of~NEC~difference), x = 0.55, y = 10.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.NEC= p.comp.NEC+ annotate("text", label = "UVR < PAR = 35.38%", x = 0.55, y = 8.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename and show plot
comp.plot.Ant.17Dec.frag48.NEC <- p.comp.NEC
comp.plot.Ant.17Dec.frag48.NEC
```


Create a custom plot of the NEC comparisons differences posterior density
```{r}
load("2017.12_Ant_frag48_posterior_comp_NEC.RData")

p.comp.NEC.diff = ggplot(comp.Ant.17Dec.frag48.NEC$diff_data, aes(x=diff)) + 
  geom_density(aes(x=diff, fill = 'grey'), alpha=0.4) + 
  stat_pointinterval(aes(y = 0.00, x = comp.Ant.17Dec.frag48.NEC$df4.s$diff),.width = c(.66, .95)) +
   geom_vline(xintercept = 0, color = "steelblue3", lty = 2, size=0.75) + theme_light()

p.comp.NEC.diff = p.comp.NEC.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
  scale_color_manual( values = c("grey", "steelblue3"))+theme(legend.position="none")
p.comp.NEC.diff = p.comp.NEC.diff + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80")) 

p.comp.NEC.diff = p.comp.NEC.diff + scale_y_continuous(name ="Differences posterior density") 
p.comp.NEC.diff = p.comp.NEC.diff + scale_x_continuous(name ="Standardized effect size")


#Rename & show plot
comp.plot.Ant.17Dec.frag48.NEC.diff <- p.comp.NEC.diff
comp.plot.Ant.17Dec.frag48.NEC.diff
```

----------------------------------------------------------------
----------------------------------------------------------------


## Create layouts and export (if required)


Create layout to view result plots side-by-side
```{r}
layout.Ant.17Dec.frag48 <- ggarrange(plot.Ant.17Dec.frag48.all, comp.plot.Ant.17Dec.frag48.EC50, plot.Ant.17Dec.frag48.diff.est, plot.Ant.17Dec.frag48.NEC, comp.plot.Ant.17Dec.frag48.NEC,
          ncol = 3, nrow = 2,
          widths = c(0.5, 0.5))
layout.Ant.17Dec.frag48
```

