---
title: "2018.11 Larval Phenanthrene 48 h fragmentation"
author: "Mikaela Nordborg"
date: "23/02/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(dplyr)
library(bayesnec) #devtools::install_github("open-AIMS/bayesnec")
require(tidyverse)
library(beepr)
inv.log10 <- function(x){10^x}
```


## Background
Analysis of data sets from A. millepora planula larvae experiments performed between 2016 and 2019 to test the effects of filtered seawater (FSW) solutions containing individual aromatic hydrocarbons in the presence and absence of ultraviolet radiation (+UV vs -UV). All analysis performed in (at least) four steps:
    - Model fitting, evaluation and interpretation of -UVR/PAR only treatment data
    - Model fitting, evaluation and interpretation of +UVR treatment data
    - Extraction of no effect concentration (NEC), 10 and 50% effect or lethal concentrations (EC/LCx) and associated 95% credible intervals.
    - Comparison of posterior distributions of extracted NEC and 50% threshold concentrations for each light treatment (+/-UV).

Compromised or invalid replicates identified prior to data import into R but removal is performed after import. Please see methods of main paper and *Table ___*, Supplementary materials for further details. Control treatment concentration-values set to 0.1 (~1/2 of the lowest treatment concentration used across all assays) to avoid potential issues with transformations after data import.Treatment concentrations log10 transformed and analysed on log-scale due to the spacing of treatment concentrations and range covered (equal to or larger than 3 orders of magnitude).


A majority of the data sets consist of binomial data and the following terms are used throughout:
    year = year and month experiment was performed
    endpoint = endpoint assessed
    factor = light treatment used
        PAR = -UVR/in the absence of UV light
        UV = +UVR/in the presence of UV light
    nom.x = nominal treatment or treatment concentration used (eg FSW or 0.01% DMSO controls)
    raw.x = time averaged, measured treatment concentration in μg L-1
    log.x = transformed, time-averaged, treatment concentrations (measured in μg L-1)
    suc = number of successes in sample (ie number of average sized larvae), generally a log10-transformation used
    tot = total number of organisms/larvae & recruits in sample at time of assessment
    prop = proportion of successes out of total tries/larvae in the sample


Data for some compounds available for several years and/or months. Each data set was analysed separately.


Analysis performed by Mikaela Nordborg and Dr. Rebecca Fisher.


## Packages used and installation of latest version of bayesnec

Analysis performed using package bayesnec and it's dependencies in R Version 4.0.3. The latest version of bayesnec and all dependencies were installed prior to start of analysis (25 April 2021).



## Analysis

### Import data, perform data preparation and check data types

Import data, wrangle and do quick initial checks
```{r}
data.Phe.18Nov.frag48.raw <- read_csv("Data/2018.11_AM_phen_frags48h.csv") %>% 
  data.frame() %>% 
  dplyr::mutate(raw.x=as.numeric(as.character(raw.x)),
                raw.x=ifelse(raw.x==0, 0.1, raw.x), # deal with 0 concentration values
                nom.x=as.factor(as.character(nom.x)),
                factor=as.factor(as.character(factor)),
                suc=as.integer(suc), # ensure integers
                log.x=log10(raw.x), # create log values (doesn't really matter if it's log or log10() unless there's a difference in the scaling of the x-data)
                tot=as.integer(tot))


save(data.Phe.18Nov.frag48.raw, file = "2018.11_Phe_data_frag48_raw.RData")

#Check that all columns have been assigned the correct data type & that adding 0.1 to raw.x controls worked
str(data.Phe.18Nov.frag48.raw)
head(data.Phe.18Nov.frag48.raw)
tail(data.Phe.18Nov.frag48.raw)
```


Check for differences between 0.01% DMSO and FSW controls
```{r}
load("2018.11_Phe_data_frag48_raw.RData")

#Remove treatment replicates from data set
data.Phe.18Nov.frag48.controls <- data.Phe.18Nov.frag48.raw %>% 
  dplyr::filter(nom.x!="Treatment")

#Plot to compare means and CIs
ggplot(data.Phe.18Nov.frag48.controls, aes(x=nom.x, y=prop, fill=factor)) + 
    geom_boxplot()

#Filer in preparation for t-tests
Phe.18Nov.frag48.controls.PAR.FSW <- data.Phe.18Nov.frag48.controls %>% 
  dplyr::filter(factor=="PAR" & nom.x=="FSW")
Phe.18Nov.frag48.controls.PAR.DMSO <- data.Phe.18Nov.frag48.controls %>% 
  dplyr::filter(factor=="PAR" & nom.x!="FSW")

Phe.18Nov.frag48.controls.UV.FSW <- data.Phe.18Nov.frag48.controls %>% 
  dplyr::filter(factor=="UVR" & nom.x=="FSW")
Phe.18Nov.frag48.controls.UV.DMSO <- data.Phe.18Nov.frag48.controls %>% 
  dplyr::filter(factor=="UVR" & nom.x!="FSW")

#Perform t-test to check for differences between control groups
brms.fit <- brm(suc | trials(tot)  ~ nom.x*factor, data = data.Phe.18Nov.frag48.controls, family = binomial())
new.dat <- data.frame(expand.grid(list(nom.x=c("FSW", "0.01% DMSO"),  "factor"=c("UVR", "PAR"),"tot"=1)))
post_preds <- posterior_epred(brms.fit, newdata=new.dat) %>% 
  data.frame

colnames(post_preds) <- paste(new.dat$nom.x, new.dat$factor)
pred_dat <-  post_preds %>% 
  pivot_longer(everything())

ggplot(pred_dat, aes(x=value)) + 
  geom_density(aes(group=name, colour=name, fill = name), alpha=0.3) +
  scale_x_continuous(labels = scales::percent, name ="Average 48 h fragmentation success") +
  scale_y_continuous(name ="Posterior probability density") +
  theme_classic() 
```


Extract the median proportion of larvae that were of average size using the posterior probability for each control data set
```{r}
quantile(post_preds[,1], c(0.025, 0.5, 0.975)) #FSW UVR
quantile(post_preds[,2], c(0.025, 0.5, 0.975)) #0.01% DMSO UVR
quantile(post_preds[,3], c(0.025, 0.5, 0.975)) #FSW PAR
quantile(post_preds[,4], c(0.025, 0.5, 0.975)) #0.01% DMSO PAR
```


Filter remaining data according to light treatment + whether replicates should be included in statistical analysis and save to RData-files:
```{r}
load("2018.11_Phe_data_frag48_raw.RData")

#Remove FSW control replicates
data.Phe.18Nov.frag48 <- data.Phe.18Nov.frag48.raw %>% 
  dplyr::filter(nom.x!="FSW")

#Create -UVR data set and prep for use in model fitting
data.Phe.18Nov.frag48.PAR.raw <- data.Phe.18Nov.frag48 %>% 
  dplyr::filter(factor=="PAR") 
data.Phe.18Nov.frag48.PAR <- data.Phe.18Nov.frag48.PAR.raw %>% 
  dplyr::filter(use_in_model=="Yes") 

#Create +UVR data set and prep for use in model fitting
data.Phe.18Nov.frag48.UV.raw <- data.Phe.18Nov.frag48 %>% 
  dplyr::filter(factor=="UVR") 
data.Phe.18Nov.frag48.UV <- data.Phe.18Nov.frag48.UV.raw %>% 
  dplyr::filter(use_in_model=="Yes") 

#check that filtering worked
View(data.Phe.18Nov.frag48.PAR)
View(data.Phe.18Nov.frag48.UV)

#Save complete data sets and data sets prepared for model fitting
save(data.Phe.18Nov.frag48.PAR.raw, data.Phe.18Nov.frag48.UV.raw, data.Phe.18Nov.frag48.PAR,data.Phe.18Nov.frag48.UV, file = "2018.11_Phe_data_frag48_filtered.RData")

load(file = "2018.11_Phe_data_frag48_filtered.RData")
```

----------------------------------------------------------------
----------------------------------------------------------------


### -UV/PAR

#### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.11_Phe_data_frag48_filtered.RData")

unique(data.Phe.18Nov.frag48.PAR$raw.x)
par(mfrow=c(2,1))
hist(data.Phe.18Nov.frag48.PAR$raw.x)
hist(data.Phe.18Nov.frag48.PAR$suc/data.Phe.18Nov.frag48.PAR$tot)
par(mfrow=c(1,1))
plot(data.Phe.18Nov.frag48.PAR$log.x, data.Phe.18Nov.frag48.PAR$prop) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


##### Fit models

###### Binomial

Fit a model-averaged NEC-model (MANEC)
```{r, eval=FALSE}
load(file = "2018.11_Phe_data_frag48_filtered.RData")
library(bayesnec)
library(beepr)
out.Phe.18Nov.frag48.PAR.all <- bnec(data = data.Phe.18Nov.frag48.PAR, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all")
save(out.Phe.18Nov.frag48.PAR.all, file = "2018.11_Phe_frag48_PAR_modfit_all.RData")
beep("mario")
```

No candidate models could be successfully fitted using the binomial distribution.



###### Betabinomial

Re-fit MANEC using a distribution appropriate for overdispersed binomial data
```{r}
load(file = "2018.11_Phe_data_frag48_filtered.RData")
library(bayesnec)
library(beepr)
out.Phe.18Nov.frag48.PAR.all.od <- bnec(data = data.Phe.18Nov.frag48.PAR, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all",
                        family = beta_binomial2)
save(out.Phe.18Nov.frag48.PAR.all.od, file = "2018.11_Phe_frag48_PAR_modfit_all_OD.RData")
beep("mario")
```

No candidate models could be successfully fitted using the betabinomial distribution.


----------------------------------------------------------------
----------------------------------------------------------------


### +UV/UV

#### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.11_Phe_data_frag48_filtered.RData")

unique(data.Phe.18Nov.frag48.UV$raw.x)
par(mfrow=c(2,1))
hist(data.Phe.18Nov.frag48.UV$raw.x)
hist(data.Phe.18Nov.frag48.UV$suc/data.Phe.18Nov.frag48.UV$tot)
par(mfrow=c(1,1))
plot(data.Phe.18Nov.frag48.UV$log.x, data.Phe.18Nov.frag48.UV$prop) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


##### Fit models

###### Binomial

Fit a model-averaged NEC-model (MANEC)
```{r, eval=FALSE}
load(file = "2018.11_Phe_data_frag48_filtered.RData")

library(bayesnec)
library(beepr)
out.Phe.18Nov.frag48.UV.all <- bnec(data = data.Phe.18Nov.frag48.UV, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all")
save(out.Phe.18Nov.frag48.UV.all, file = "2018.11_Phe_frag48_UV_modfit_all.RData")
beep("mario")
```

No candidate models could be successfully fitted using the binomial distribution.


###### Betabinomial

Re-fit MANEC using a distribution appropriate for overdispersed binomial data
```{r}
load(file = "2018.11_Phe_data_frag48_filtered.RData")
library(bayesnec)
library(beepr)
out.Phe.18Nov.frag48.UV.all.od <- bnec(data = data.Phe.18Nov.frag48.UV, 
                        x_var = "log.x", 
                        y_var = "suc", 
                        trials_var = "tot",
                        model = "all",
                        family = beta_binomial2)

save(out.Phe.18Nov.frag48.UV.all.od, file = "2018.11_Phe_frag48_UV_modfit_all_OD.RData")
beep("mario")
```


Check RHat values to discard bad candidate model fits
```{r}
load("2018.11_Phe_frag48_UV_modfit_all_OD.RData")

rhat(out.Phe.18Nov.frag48.UV.all.od, rhat_cutoff = 1.03)
```


Check chain mixing for remaining candidate models
```{r}
load("2018.11_Phe_frag48_UV_modfit_all_OD.RData")

check_chains(out.Phe.18Nov.frag48.UV.all.od, filename = "2018.11_Phe_frag48_UV_chains_modfit_all_OD") #change this if any candidate models were discarded based on Rhat: out.Phe.18Nov.frag48.UV.all.od2
out.Phe.18Nov.frag48.UV.all.od$mod_stats
summary(out.Phe.18Nov.frag48.UV.all.od)
```

*Any evidence of non-convergence, poor chain mixing or autocorrelation?*
    - No.


```{r}
plot(out.Phe.18Nov.frag48.UV.all.od, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```

    
Check if model median, credible intervals and NEC estimates are reasonable for candidate models compared to the raw data
```{r}
load("2018.11_Phe_frag48_UV_modfit_all_OD.RData")
pdf("2018.11_Phe_frag48_UV_modfitplots_all_OD.pdf")
plot(out.Phe.18Nov.frag48.UV.all.od, all_models = TRUE, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
dev.off()
```

*Based on individual candidate model fit-plots the following candidate models should be excluded from the OD MANEC:*
    - All models should be excluded



#### Plot MANEC model fits alongside raw data
##### Plot raw data for comparison with other compounds

```{r}
load("2018.11_Phe_data_frag48_filtered.RData")
#load("2018.11_Phe_frag48_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


#p.all= p.all+  geom_ribbon(aes(x=10^pred.Phe.18Nov.frag48.PAR.inv$x, ymin=pred.Phe.18Nov.frag48.PAR.inv$Q2.5, ymax=pred.Phe.18Nov.frag48.PAR.inv$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
#p.all= p.all+  geom_ribbon(aes(x=10^pred.Phe.18Nov.frag48.UV.inv$x, ymin=pred.Phe.18Nov.frag48.UV.inv$Q2.5, ymax=pred.Phe.18Nov.frag48.UV.inv$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


#p.all= p.all+ geom_line(aes(x=10^pred.Phe.18Nov.frag48.PAR.inv$x, y=pred.Phe.18Nov.frag48.PAR.inv$Estimate), color = 'grey30', size=0.5)
#p.all= p.all+ geom_line(aes(x=10^pred.Phe.18Nov.frag48.UV.inv$x, y=pred.Phe.18Nov.frag48.UV.inv$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = data.Phe.18Nov.frag48.PAR, aes(x = raw.x, y = prop, colour=factor(factor), shape = factor(factor), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.02))
p.all= p.all+ geom_point(data = data.Phe.18Nov.frag48.UV, aes(x = raw.x, y = prop, colour=factor(factor), shape = factor(factor), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.02))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~"L"^{-1})
              y=expression(48~h~fragmentation~("%")),
              subtitle="a)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue"))
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.09, 30000), trans="log10", breaks = c(0.1, 1, 10, 100, 1000, 10000), labels = c(0, 1, 10, 100, 1000, 10000))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot.Phe.18Nov.frag48.all <- p.all
plot.Phe.18Nov.frag48.all
```

